Feasibility of Harvesting Power To Run A Domestic Water Meter Using Streaming Cell Technology

### 2014-09-11 paper.tex
Added power vs pressure graph

    \section{Readily Attainable Streaming Cell Power} \label{sect:streamingCell}
    In~\cite{Gu2000}, the authors employ a relatively simple parallel plate design to create a streaming cell.
    They glued plastic shims between parallel plates of glass, providing a simple way of controlling channel height.
    Using that method, the authors fabricated three cells with channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
    Each of the channels were \SI{3}{\centi\metre} long and had a inner width of \SI{1}{\centi\metre}.

    \begin{figure}
        \begin{center}
        \includegraphics[width=\linewidth]{Photo_streamingPotential_Assembly_Step3.JPG}
        \end{center}
        \caption{One of our ten constructed streaming cells mounted in an acrylic holder. Copper wires have been epoxied into each side to provide a means of measuring the developed potential across the cell. The plastic shims are visible as the orange strips at each side of the cell.}
        \label{fig:cell}
    \end{figure}

@@

@@

@@

    \section{Results}
    \label{sect:results}

>>>>

    \section{Readily Attainable Streaming Cell Power} \label{sect:streamingCell}
    \begin{figure}
        \begin{center}
        \includegraphics[width=\linewidth]{Photo_streamingPotential_Assembly_Step3.JPG}
        \end{center}
        \caption{One of our ten constructed streaming cells mounted in an acrylic holder. Copper wires have been epoxied into each side to provide a means of measuring the developed potential across the cell. The plastic shims are visible as the orange strips at each side of the cell.}
        \label{fig:cell}
    \end{figure}

    In~\cite{Gu2000}, the authors employ a relatively simple parallel plate design to create a streaming cell.
    They glued plastic shims between parallel plates of glass, providing a simple way of controlling channel height.
    Using that method, the authors fabricated three cells with channel heights of \SI{50}{\micro\metre}, \SI{100}{\micro\metre} and \SI{150}{\micro\metre}.
    Each of the channels were \SI{3}{\centi\metre} long and had a inner width of \SI{1}{\centi\metre}.

@@

    Based on measurements of the \SI{52}{\micro\meter} channel we estimate the amount of electrical power available for harvesting.
    Fig.~\ref{fig:equivalentCircuit} shows the equivalent circuit for a streaming potential cell delivering a streaming current ($I_{S}$).
    The the streaming potential ($V_{S}$) was measured with no load restance ($R_{L}$) due to the use of the E5270 preventing load current being drawn.
    The dimensions of the cell together with the conductivity of the working fluid give the cell an internal resistance ($R_{ch}$) of approximately \SI{30}{\giga\ohm}.
    Using these parameters, the available output power from the cell has been calculated and is presented in Fig.~\ref{fig:cellPowerPressure} with respect to the applied pressuse.

@@

    \begin{figure}
        \begin{center}
        \includegraphics[width=\linewidth]{StreamingCell_EquivalentCircuit}
        \end{center}
        \caption{Equivalent circuit of the streaming potential cell.
        Streaming current is produced by the current source and is denoted $I_{S}$.
        The internal channel resistance is $R_{ch}$ and an external load is denoted as $R_{L}$}
        \label{fig:equivalentCircuit}
    \end{figure}

    \begin{figure}
        \begin{center}
        \includegraphics[width=\linewidth]{graph_powerPressure}
        \end{center}
        \caption{Maximum power available to an external load placed across the \SI{52}{\micro\meter} cell as a function of pressure differential. Power has been calculated using a load resistance of \SI{30}{\giga\ohm} where only half of total power is available to the load. Note that the units of power are expressed in picoWatts.}
        \label{fig:cellPowerPressure}
    \end{figure}

@@
